Microxanox - an R package for simulating an $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states.

### 2022-05-02 inst/manuscript/manuscript_microxanox.Rmd
Update manuscript_microxanox.Rmd
Minor Changes

---
title: "Microxanox - an R package for simulating an $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: |
  Ca. 100 words.
bibliography: manuscript_bibliography.bib
journal: "SoftwareX"
date: "`r Sys.Date()`"

@@

# Citation settings
nocite: '@Bush2017'
linkcolor: blue
link-citations: yes
---

@@

# TODO
- **update links**
- **update crossref**

>>>>

---
title: "Microxanox - an R package for simulating an $MICR$obial ecosystem that can occupy $OX$ic or $ANOX$ic states."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch;  Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: |
  Ca. 100 words.
journal: "SoftwareX"
date: "`r Sys.Date()`"

@@

# Citation settings
bibliography: bibliography.bib
nocite: '@Bush2017'
linkcolor: blue
link-citations: yes
---

@@

# \color{red}TODO
- \color{red}**update links** 
- \color{red}**update cross references**
\pagebreak
